Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
skeleton abstract, remove table of contents

\begin{abstract}
  Arithmetic geometry group at the Emory University Number Theory
	REU.
\end{abstract}

@@

\tableofcontents

>>>>

\begin{abstract}
  Generalizing the classical theorems of Max Noether and Karl 
	Petri, we describe generators and relations for the spin canonical
	ring of a stacky curve equipped with an arbitrary log divisor. As
	an application, we bound the generation degrees and relation
	degrees for graded rings of modular forms of arbitrary integral
	weight arising from finite-area quotients of the upper half-
	plane by Fuchsian groups.
\end{abstract}

@@
